\chapter{Third-Party Code and Libraries}

\textbf{Please note: } There are libraries and frameworks included with Laravel, such as Vue.js and Axios, but they are unused. Only libraries and frameworks listed here have been used in Railrota. They are however, compatible with Laravel's MIT licensing.

\section{Laravel Framework}
Laravel Framework - Laravel is the main PHP web framework that empowers the application. This includes features commonly used by the Railrota application, such as the Eloquent ORM for working with the database, the Carbon datetime library, the Laravel Blade templating engine, the Artisan command line tool, and Laravel Mix for compiling front-end assets. The framework is released using the MIT license. This framework was used without modification. 

https://github.com/laravel/laravel

\section{Laravel Telescope}
Laravel Telescope is an optional library for Laravel to aid with debugging. The library is released using the MIT license. This library was used without modification.

https://github.com/laravel/telescope

\section{dompdf-laravel}
DOMPDF Wrapper for Laravel - HTML/CSS rendering engine used for converting webpages into PDF pages. Laravel wrapper for the DOMPDF library. The library is released using the MIT license. This library was used without modification.

https://github.com/barryvdh/laravel-dompdf

\section{Sami}
Sami API Documentation Generator - A standalone tool used for compiling PHPDoc / docblock comments into full documentation in HTML form. The tool is released using the MIT license. This tool was used without modification.

https://github.com/FriendsOfPHP/Sami

\section{PHPUnit}
PHPUnit - unit testing suite included with Laravel, but as it is used in development and not in production, included as a separate entry here. The framework is released under the BSD-3 license. This framework was used without modification.

https://github.com/sebastianbergmann/phpunit

\section{Bootstrap 4}
Bootstrap - HTML/CSS and JavaScript framework for responsive web design. This framework was released under the MIT license. This framework was used without modification.

https://github.com/twbs/bootstrap

\section{jQuery}

jQuery - JavaScript library for DOM manipulation and used by Bootstrap. This library was released under the MIT license. This framework was used without modification.

https://github.com/jquery/jquery 

\section{Font Awesome}

Font Awesome - CSS framework used for inserting icons into front-end UIs. This framework's code is licensed under the MIT license, with the icons being released under the CC BY 4.0 License. This framework is used without modification. More information can be found under the framework's LICENSE file.

https://github.com/FortAwesome/Font-Awesome