\thispagestyle{empty}

%TC:ignore

\begin{center}
    {\LARGE\bf Acknowledgements}
\end{center}

\noindent I dedicate this work to my late aunt, Deborah Jones, who tragically passed away in June 2019 during her courageous and tenacious fight against cancer. On top of being a wonderful aunt and akin to a second mother, you were inexplicably supportive and reassuring in every moment of my academic career. I miss you greatly.

\noindent I am grateful for the endless support and empathy provided by my colleagues in the Department of Computer Science at Aberystwyth University throughout my most challenging year in academia thus far. In particular to my supervisor Richard Shipman who enthusiastically accepted me onto the project without hesitation and ensuring that I remained on-target and focused despite some initial setbacks, and to my personal tutor Edel Sherratt, who was always available to offer much-needed motivation and a listening ear at a moment's notice.

\noindent Furthermore, I wish to extend a heartfelt thanks to my family and friends throughout the world for their support, donations, and words of encouragement. I could not have done it without you.

\noindent Finally, I would like to express my further gratitude to those I have had the privilege to work alongside at Aberystwyth University, Aberystwyth University Students' Union, Aberystwyth Nightline, the Nightline Association, and the National Union of Students. You enabled me to have a positive and profound impact in their lives and wellbeing of my fellow students throughout the year, and for that I am extremely thankful.

\noindent It has been an unrivalled privilege to have spent the majority of the last five years studying in idyllic West Wales, enrolled at a university brimming with history, expertise, and compassion. Aberystwyth will undoubtedly be a place I shall always call home.

\vspace{15mm}

\begin{center}
\noindent Thank you very much.

\noindent \textit{Diolch yn fawr iawn.}
\end{center}
%TC:endignore